---
title: "Politicians"
author: "Stefano Falconi"
date: "13/6/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Part 1
What can be observed is that for the group of politicians starting their
mandates, there is no room for "Executive Councils". Only for the years 1803,
1827 and 1839, three individuals started their mandate as "Small Council".
Apparently, this position lost relatively importance. Likewise,for the second 
group - those finishing their mandate - "Small Councils" never appeared.

For this second group, between the years 1840 and 1939, there were seven
periods of massive retirements (about 200 politicians). Past 1939, this
seoond group had retirement of smaller size (50). For the first group, the
only three massive "starters" occurred only in the XIX Century and no more 
than three massive occurrences. Massive starters included about 130 poloiticians
at once for both, Cantonal and Gran Council.

## Part 2
Apparently, involvement of women into politics is relatively low as can be
observed in the two plots, one for starting mandates and another for ending
mandate.

## Part 3
The table shows one elected candidate for the EVP, FDP, and LdU parties for
year 2000 and five candidates from the SP party elected for same year.

## Part 4
In the past three years four parties have had more elected candidates for the 
Cantonal Council: EDU, BDT, SP, and AL

## Part 5
The average life span is 80.2 years. It does change by title. The boxplot gives 
a clue about the life span difference between politicians with title compared
to those without title. The median´s boxplot value almost coincides with the
mean's life span for the whole group (title + no title), whereas the median 
for the no "formally" educated politicians was lower.

It was hard to tell without the plot any potential difference. My expectation 
agrees with the results of the Kruskal-Wallis test of difference in life span 
from the two groups.  

## Part 6
It was interesting to observe how in the first case - before 1918 - the medians
of both boxplots (formally educated vs no title) were similar. The Kruskal-Wallis
test confirmed such visual equality (p-value = 0.4359).

For the secon group - after 1918, the difference in medians resembled that from 
above (Part 5). The p-value was so low that it was a strong evidence for 
rejecting the null hypothesis pf "no difference in life span among politicians 
with title vs politicians with no title".

## Part 7
The ten politicians with most mandates are the following:
                                                               
Six terms: K. Arbenz, S.Spöngli, H. Weiss, J. Hatt, E.Sulzer, H.Toggenburger;
Five terms: W. Trostel, M. Sulzer, J.Schenk, J.Zollinger

## Part 9
Several politicians have been affiliiated to different parties along the years. 
For instance: E. Bachmann, E. Kessler, Alfred Messer have been affiliated to four
different parties and Willy Trustel and Arthur Bachmann to five different parties.


```{r}

library(tidyverse)
library(dplyr)
library(tidylog)
library(tidyr)
library(lubridate)
library(odbc)
library(RSQLite)
library(DBI)
library(stringr)
library(ggpubr)
library(visdat)


zpoliticians_db <- dbConnect(RSQLite::SQLite(), "zh_politicians.db")

 
 dbListTables(zpoliticians_db) 

mandato<-DBI::dbGetQuery(zpoliticians_db, 
"SELECT DISTINCT ID, PERSON_ID, ASSEMBLY, MANDATE_START_DAY,
MANDATE_START_MONTH, MANDATE_START_YEAR, MANDATE_END_DAY, 
MANDATE_END_MONTH, MANDATE_END_YEAR FROM MANDATES;")   
 
 mandato_p<-DBI::dbGetQuery(zpoliticians_db,
"SELECT DISTINCT ID, LASTNAME, FIRSTNAME, TITLE, GENDER, YEAR_OF_BIRTH,
YEAR_OF_DEATH FROM PERSONS;")                          
 
  mandato_a<-DBI::dbGetQuery(zpoliticians_db,
"SELECT DISTINCT ID, MANDATE_ID, PERSON_ID, PARTY, AFFILIATION_START_DAY, 
AFFILIATION_START_MONTH, AFFILIATION_START_YEAR, AFFILIATION_END_DAY,
AFFILIATION_END_MONTH, AFFILIATION_END_YEAR FROM AFFILIATIONS;")
 
mandato_a_red<- mandato_a[,c(3,2)]


  
 mandato_pol<-mandato %>% 
select(ASSEMBLY,MANDATE_START_DAY, MANDATE_START_MONTH, MANDATE_START_YEAR)%>%
group_by(ASSEMBLY,MANDATE_START_DAY, MANDATE_START_MONTH)%>% 
filter(MANDATE_START_YEAR %in% c(1803,1805,1807,1808,1809,1811,1813,1814,
1815,1816,1817,1818,1819,1820,1821,1822,1823,1824,1825,1826,1827,1828,1829,
1830,1831,1832,1833,1834,1835,1836,1837,1838,1839,1840,1841,1842,1843,1844,
1845,1846,1847,1848,1849,1850,1851,1852,1853,1854,1855,1856,1857,1858,1859,
1860,1861,1862,1863,1864,1865,1866,1867,1868,18691870,1871,1872,1873,1874,
1875,1876,1877,1878,1879,1880,1881,1882,1883,1884,1885,1886,1887,1888,1889,
1890,1891,1892,1893,1894,1895,1896,1897,1898,1899,1900,1901,1902,1903,1904,
1905,1906,1907,1908,1909,1928,1929,1930,1931,1932,1933,1934,1935,1936,1937,
1938,1939,1940,1941,1942,1943,1944,1945,1946,1947,1948,1949,1950,1951,1952,
1953,1954,1955,1956,1957,1958,1959,1960,1961,1962,1963,1964,1965,1966,1967,
1968,1969,1970,1971,1973,1974,1975,1976,1977,1978,1979,1980,1981,1982,1983,
1984,1985,1986,1987,1988,1989,1990,1991,1992,1993,1994,1995,1996,1997,1998,
1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,
014,2015,2016,2017,2018), ASSEMBLY %in% c("Cantonal Council","Executive
Council", "Grand Council", "Small Council") )%>%
count(MANDATE_START_YEAR, name="cambios") %>%
arrange(MANDATE_START_YEAR)
View(mandato_pol)
 
ggplot(mandato_pol, aes(x=MANDATE_START_YEAR, y=cambios, color=ASSEMBLY))+
  geom_point() + geom_line(colour="blue")+facet_wrap(.~ ASSEMBLY, ncol = 4)+
 scale_x_continuous(name = "Mandate starts", limits = c(1800, 2020)) +
  scale_y_continuous(name = "Period change", limits = c(0, 150))



 
mandato_pol_end<-mandato %>%
select(ASSEMBLY,MANDATE_END_DAY, MANDATE_END_MONTH, MANDATE_END_YEAR)%>%
group_by(ASSEMBLY,MANDATE_END_DAY, MANDATE_END_MONTH)%>% 
filter(MANDATE_END_YEAR %in% c(1804,1805,1807,1808,1809,1810,1811,1812,
1813,1814,1815,1816,1817,1818,1819,1820,1821,1822,1824,1825,1826,1827,1828,
1829,1830,1831,1832,1833,1834,1835,1836,1837,1838,1839,1840,1841,1842,1843,
1844,1845,1846,1847,1848,1849,1850,1851,1852,1853,1854,1855,1856,1857,1858,
1859,1860,1861,1862,1863,1864,1865,1866,1867,1868,1869,1870,1871,1872,1873,
1874,1875,1876,1877,1878,1879,1880,1881,1882,1883,1884,1885,1886,1887,1888,
1889,1890,1891,1892,1893,1894,1895,1896,1897,1898,1899,1900,1901,1902,1903,
1904,1905,1906,1907,1908,1909,1910,1911,1912,1913,1914,1915,1916,1917,1918,
1919,1920,1921,1922,1923,1924,1925,1926,1927,1928,1929,1930,1931,1932,1933,
1934,1935,1936,1937,1938,1939,1940,1941,1942,1943,1944,1945,1946,1947,1948,
1949,1950,1951,1952,1953,1954,1955,1956,1957,1958,1959,1960,1961,1962,1963,
1964,1965,1966,1967,1968,1969,1970,1971,1972,1973,1974,1975,1976,1977,1978,
1979,1980,1981,1982,1983,1984,1985,1986,1987,1988,1989,1990,1991,1992,1993,
1994,1995,1996,1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,
2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019), ASSEMBLY %in% 
  c("Cantonal Council", "Executive Council", "Grand Council", "Small 
  Council")) %>%
count(MANDATE_END_YEAR, name="retiro") %>%
arrange(MANDATE_END_YEAR)
View(mandato_pol_end)


ggplot(mandato_pol_end, aes(x=MANDATE_END_YEAR, y=retiro, color=ASSEMBLY))+
  geom_point() + geom_line(colour="red")+facet_wrap(.~ASSEMBLY, ncol = 4)+
 scale_x_continuous(name = "Mandate starts", limits = c(1800, 2020)) +
  scale_y_continuous(name = "Period change", limits = c(0, 135))




mandato_p$PERSON_ID<-mandato_p$ID
View(mandato_p)
mandato_p<-mandato_p[,c(13,2:12)]
mandato_p_ij<-inner_join(mandato, mandato_p, by=("PERSON_ID"))
mandato_p_ij<- mandato_p_ij %>% distinct()
View(mandato_p_ij)




mandato_p_ij_init<-mandato_p_ij %>%                                                     select(ASSEMBLY, GENDER, MANDATE_START_DAY, MANDATE_START_MONTH, 
MANDATE_START_YEAR)%>%
group_by(ASSEMBLY, GENDER, MANDATE_START_DAY, MANDATE_START_MONTH)%>%                                filter(MANDATE_START_YEAR %in% c(1803,1805,1807,1808,1809,1811,1813,1814,
1815,1816,1817,1818,1819, 1820,1821,1822,1823,1824,1825,1826,1827,1828,1829,
1830,1831,1832,1833,1834,1835,1836,1837,1838,1839,1840,1841,1842,1843,1844,
1845,1846,1847,1848,1849,1850, 1851,1852,1853,1854,1855,1856,1857,1858,1859,
1860,1861,1862,1863,1864,1865,1866,1867,1868,18691870,1871,1872,1873,1874,
1875,1876,1877,1878,1879,1880,1881,1882,1883,1884,1885,1886,1887,1888,1889,
1890,1891,1892,1893,1894,1895,1896,1897,1898,1899,1900,1901,1902,1903,1904,
1905,1906,1907,1908,1909,1928,1929,1930,1931,1932,1933,1934,1935,1936,1937,
1938,1939,1940,1941,1942,1943,1944,1945,1946,1947,1948,1949,1950,1951,1952,
1953,1954,1955,1956,1957,1958,1959,1960,1961,1962,1963,1964,1965,1966,1967,
1968,1969,1970,1971,1972,1973,1974,1975,1976,1977,1978,1979,1980,1981,1982,
1983,1984,1985,1986,1987,1988,1989,1990,1991,1992,1993,1994,1995,1996,1997,
1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,
2013,2014,2015,2016,2017,2018))%>%
count(MANDATE_START_YEAR, name="cambios") %>%
arrange(MANDATE_START_YEAR)

View(mandato_p_ij_init)

ggplot(mandato_p_ij_init,aes(x = MANDATE_START_YEAR, y =cambios, color=ASSEMBLY)) +
geom_point()+ geom_line()+
facet_grid(ASSEMBLY ~ GENDER)+
 theme(axis.text.x = element_text(angle = -60, vjust = 0.5, hjust=0))


mandato_p_ij_end <-mandato_p_ij %>%
select(ASSEMBLY,GENDER, MANDATE_END_DAY, MANDATE_END_MONTH, MANDATE_END_YEAR)%>%
group_by(ASSEMBLY,GENDER, MANDATE_END_DAY, MANDATE_END_MONTH)%>% 
filter(MANDATE_END_YEAR %in% c(1804,1805,1807,1808,1809,1810,1811,1812,
1813,1814,1815,1816,1817,1818,1819,1820,1821,1822,1824,1825,1826,1827,1828,
1829,1830,1831,1832,1833,1834,1835,1836,1837,1838,1839,1840,1841,1842,1843,
1844,1845,1846,1847,1848,1849,1850,1851,1852,1853,1854,1855,1856,1857,1858,
1859,1860,1861,1862,1863,1864,1865,1866,1867,1868,1869,1870,1871,1872,1873,
1874,1875,1876,1877,1878,1879,1880,1881,1882,1883,1884,1885,1886,1887,1888,
1889,1890,1891,1892,1893,1894,1895,1896,1897,1898,1899,1900,1901,1902,1903,
1904,1905,1906,1907,1908,1909,1910,1911,1912,1913,1914,1915,1916,1917,1918,
1919,1920,1921,1922,1923,1924,1925,1926,1927,1928,1929,1930,1931,1932,1933,
1934,1935,1936,1937,1938,1939,1940,1941,1942,1943,1944,1945,1946,1947,1948,
1949,1950,1951,1952,1953,1954,1955,1956,1957,1958,1959,1960,1961,1962,1963,
1964,1965,1966,1967,1968,1969,1970,1971,1972,1973,1974,1975,1976,1977,1978,
1979,1980,1981,1982,1983,1984,1985,1986,1987,1988,1989,1990,1991,1992,1993,
1994,1995,1996,1997,1998,1999,2000,2001,2002,2003,2004,2005,2006,2007,2008,
2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019), ASSEMBLY %in% 
  c("Cantonal Council", "Executive Council", "Grand Council", "Small 
  Council")) %>%
count(MANDATE_END_YEAR, name="retiro") %>%
arrange(MANDATE_END_YEAR)
View(mandato_p_ij_end)



ggplot(mandato_p_ij_end, aes(x = MANDATE_END_YEAR, y =retiro, 
    color=ASSEMBLY)) +
geom_point()+ geom_line(colour="brown")+facet_grid(ASSEMBLY ~ GENDER) +
theme(axis.text.x = element_text(angle = -60, vjust = 0.5, hjust=0))
   
      
      
mandato_a<-mandato_a[,c(3:10)]
View(mandato_a)
mandato<-mandato[,c(2:9)]
View(mandato)
View(mandato_a_ij)      
mandato_a_ij<-inner_join(mandato_a, mandato,by=("PERSON_ID"))
mandato_a_ij<- mandato_a_ij %>% distinct()
vis_miss(mandato_a_ij)
View(mandato_a_ij)

mandato_2000_cc<-mandato_a_ij %>%
 select(PERSON_ID,ASSEMBLY, PARTY,MANDATE_START_YEAR) %>%
group_by(PARTY,ASSEMBLY) %>%
filter(MANDATE_START_YEAR==2000, ASSEMBLY %in% c("Cantonal Council",
  "Grand Council", "Executive Council")) %>%
 count(MANDATE_START_YEAR, name = "frequency") %>%
mutate(relative_frequency = round(100*frequency/sum(frequency)))
 
 View(mandato_2000_cc)
 ggplot(mandato_2000_cc,aes(x = "", y = frequency, fill = PARTY)) +
    geom_col(alpha = 0.7) +
    coord_polar("y", start = 0, direction = -1) +
    geom_text(aes(label = paste0(relative_frequency, "%")),
              position = position_stack(vjust = 0.5),
              size = 7) +
    labs(title = "Party Participation in Election",
         subtitle = "Cantonal Council",
         fill = "MANDATE_START_YEAR") + theme_void()
 
 
  
  
  mandato_assembly_evolution<-mandato_a_ij %>%
 select(PERSON_ID,ASSEMBLY, PARTY,MANDATE_START_YEAR) %>%
 group_by(PARTY,ASSEMBLY) %>%
     filter(MANDATE_START_YEAR %in% c(1803,1805,1807,1808,1809,1811,1813,1814,1815,1816,1817,1818,1819,1820,1821,
1822,1823,1824,1825,1826,1827,1828,1829,1830,1831,1832,1833,1834,1835,1836,
1837,1838,1839,1840,1841,1842,1843,1844,1845,1846,1847,1848,1849,1850,1851,
1852,1853,1854,1855,1856,1857,1858,1859,1860,1861,1862,1863,1864,1865,1866,
1867,1868,18691870,1871,1872,1873,1874,1875,1876,1877,1878,1879,1880,1881,
1882,1883,1884,1885,1886,1887,1888,1889,1890,1891,1892,1893,1894,1895,1896,
1897,1898,1899,1900,1901,1902,1903,1904,1905,1906,1907,1908,1909,1928,1929,
1930,1931,1932,1933,1934,1935,1936,1937,1938,1939,1940,1941,1942,1943,1944,
1945,1946,1947,1948,1949,1950,1951,1952,1953,1954,1955,1956,1957,1958,1959,
1960,1961,1962,1963,1964,1965,1966,1967,1968,1969,1970,1971,1973,1974,1975,
1976,1977,1978,1979,1980,1981,1982,1983,1984,1985,1986,1987,1988,1989,1990,
1991,1992,1993,1994,1995,1996,1997,1998,1999,2000,2001,2002,2003,2004,2005,
2006,2007,2008,2009,2010,2011,2012,2013, 2014, 2015 ,2016, 2017,2018), 
ASSEMBLY %in% c("Cantonal Council",
  "Grand Council", "Executive Council"))%>%
  count(MANDATE_START_YEAR, name = "frequency") %>%
mutate(relative_frequency = round(100*frequency/sum(frequency))) %>%
    arrange(desc(MANDATE_START_YEAR))
 View(mandato_assembly_evolution)
  
ggplot(mandato_assembly_evolution, aes(x = MANDATE_START_YEAR, y = frequency, 
    colour = ASSEMBLY)) +
     geom_point() +
     geom_line() +
     labs(title = "Assembly Composition",
          caption = "Evolution of Composition",
          x = "Assembly",
          y = "Evolution",
          colour = "ASSEMBLY") +
     theme_minimal()



View(mandato_p)
mandato_p_sina<-subset(mandato_p, YEAR_OF_DEATH!="")
mandato_p_sina$YEAR_OF_DEATH<-as.integer(mandato_p_sina$YEAR_OF_DEATH)
mandato_p_sina$survival<-mandato_p_sina$YEAR_OF_DEATH-mandato_p_sina$YEAR_OF_BIRTH

View(mandato_p_sina)
 
mean(mandato_p_sina$survival)


mandato_p_sina$doctores<-gsub("[^D]", "",mandato_p_sina$TITLE)
View(mandato_p_sina)


mandato_p_sina$TITLE[mandato_p_sina$TITLE==""]<-0
View(mandato_p_sina)
Do<-mandato_p_sina %>%
     select(survival, doctores)%>%
     group_by(survival) %>%
     filter(doctores=="D")
View(Do)
 controlo<-mandato_p_sina %>%
     select(survival, TITLE)%>%
     group_by(survival) %>%
     filter(TITLE==0)
view(controlo)
 controlo$TITLE,l
   group_by(survival) %>%
    filter(TITLE==0)
View(controlo)
controlo$TITLE<-as.character(controlo$TITLE)

ctrolo<-controlo
dro<-Do
View(ctrolo)
 View(dro)
 ctrolo$group<-ctrolo$TITLE
 dro$group<-dro$doctores
 View(dro)
 View(ctrolo)
 ctrolo<-ctrolo[,c(1,3)]
 View(ctrolo)
 dro<-dro[,c(1,3)]
 View(dro)



my_data_bro<-bind_rows(dro,ctrolo)
 ggboxplot(my_data_bro, x = "group", y = "survival", 
          color = "group", palette = c("#00AFBB", "#E7B800"),
     order = c("0", "D"),
         ylab = "Survival_age", xlab = "Education")+
   scale_y_continuous(name = "Survival age", limits = c(0, 100))

 
 kruskal.test(survival ~ group, data = my_data_bro)








 ggplot(data = mydata, mapping = aes(x=survival, colour = grupos)) + 
    geom_histogram(bins = 10) +
    theme_bw() + geom_text(aes(label = scales::percent(Prop)), position = position_stack(.5)) +     facet_grid(. ~ grupos) +
    theme(legend.position = "none")

  
kruskal.test(survival ~ grupos, data = mydata)  









politicians_b1918<-subset(mandato_p, BORN_BEFORE_1918==TRUE)
View(politicians_b1918)
politicians_a1918<-subset(mandato_p, BORN_AFTER_1918==TRUE)
View(politicians_a1918)
politicians_a1918_sina<-subset(politicians_a1918, YEAR_OF_DEATH!="NA")
politicians_b1918_sina<-subset(politicians_b1918, YEAR_OF_DEATH!="NA")
View(politicians_a1918_sina)
politicians_a1918_sina$survival<-politicians_a1918_sina$YEAR_OF_DEATH-politicians_a1918_sina$YEAR_OF_BIRTH
View(politicians_a1918_sina)
politicians_a1918_sina$TITLE[politicians_a1918_sina$TITLE==""]<-0
politicians_a1918_sina$doctores<-gsub("[^D]", "",politicians_a1918_sina$TITLE)
View(politicians_a1918_sina)
D<-politicians_a1918_sina %>%
     select(survival, doctores)%>%
     group_by(survival) %>%
     filter(doctores=="D")
View(D)
 View(politicians_a1918_sina)
 control<-politicians_a1918_sina %>%
     select(survival, TITLE)%>%
   group_by(survival) %>%
    filter(TITLE==0)

ctrol<-control
control$TITLE<-as.character(control$TITLE)
dr<-D
View(ctrol)
 View(dr)
 ctrol$group<-ctrol$TITLE
 dr$group<-dr$doctores
 View(dr)
 View(ctrol)
 ctrol<-ctrol[,c(1,3)]
 View(ctrol)
 dr<-dr[,c(1,3)]
 View(dr)



 ggboxplot(my_data_br, x = "group", y = "survival", 
         color = "group", palette = c("#00AFBB", "#E7B800"),
          order = c("0", "D"),
          ylab = "Survival_age", xlab = "Education")+
   scale_y_continuous(name = "Survival age", limits = c(0, 100))
   
 kruskal.test(survival ~ group, data = my_data_br)



 
 
politicians_a1918<-subset(mandato_p, BORN_AFTER_1918==TRUE)
politicians_b1918_sina<-subset(politicians_b1918, YEAR_OF_DEATH!="NA")
politicians_b1918_sina$survival<-politicians_b1918_sina$YEAR_OF_DEATH-politicians_b1918_sina$YEAR_OF_BIRTH
View(politicians_b1918_sina)
politicians_b1918_sina$TITLE[politicians_b1918_sina$TITLE==""]<-0
politicians_b1918_sina$doctores<-gsub("[^D]", "",politicians_b1918_sina$TITLE)
View(politicians_b1918_sina)
Dr<-politicians_b1918_sina %>%
     select(survival, doctores)%>%
     group_by(survival) %>%
     filter(doctores=="D")
View(Dr)
 View(politicians_b1918_sina)
 controles<-politicians_b1918_sina %>%
     select(survival, TITLE)%>%
   group_by(survival) %>%
    filter(TITLE==0)

ctrols<-controles
controles$TITLE<-as.character(controles$TITLE)
drs<-Dr
View(ctrols)
 View(drs)
 ctrols$group<-ctrols$TITLE
 drs$group<-drs$doctores
 View(drs)
 View(ctrols)
 ctrols<-ctrols[,c(1,3)]
 View(ctrols)
 drs<-drs[,c(1,3)]
 View(drs)



my_data_brs<-bind_rows(drs,ctrols)
 ggboxplot(my_data_brs, x = "group", y = "survival", 
         color = "group", palette = c("#00AFBB", "#E7B800"),
          order = c("0", "D"),
          ylab = "Survival_age", xlab = "Education")+
   scale_y_continuous(name = "Survival age", limits = c(0, 100))
   
 kruskal.test(survival ~ group, data = my_data_brs)




 
 
 
 
 
 
  most_mandates<-mandato_p_ij %>%
 select(PERSON_ID,FIRSTNAME,LASTNAME,MANDATE_START_YEAR) %>%
 group_by(PERSON_ID,FIRSTNAME, LASTNAME) %>%
     filter(MANDATE_START_YEAR %in% c(1803,1805,1807,1808,1809,1811,1813,1814,1815,1816,1817,1818,1819,1820,1821,
1822,1823,1824,1825,1826,1827,1828,1829,1830,1831,1832,1833,1834,1835,1836,
1837,1838,1839,1840,1841,1842,1843,1844,1845,1846,1847,1848,1849,1850,1851,
1852,1853,1854,1855,1856,1857,1858,1859,1860,1861,1862,1863,1864,1865,1866,
1867,1868,18691870,1871,1872,1873,1874,1875,1876,1877,1878,1879,1880,1881,
1882,1883,1884,1885,1886,1887,1888,1889,1890,1891,1892,1893,1894,1895,1896,
1897,1898,1899,1900,1901,1902,1903,1904,1905,1906,1907,1908,1909,1928,1929,
1930,1931,1932,1933,1934,1935,1936,1937,1938,1939,1940,1941,1942,1943,1944,
1945,1946,1947,1948,1949,1950,1951,1952,1953,1954,1955,1956,1957,1958,1959,
1960,1961,1962,1963,1964,1965,1966,1967,1968,1969,1970,1971,1973,1974,1975,
1976,1977,1978,1979,1980,1981,1982,1983,1984,1985,1986,1987,1988,1989,1990,
1991,1992,1993,1994,1995,1996,1997,1998,1999,2000,2001,2002,2003,2004,2005,
2006,2007,2008,2009,2010,2011,2012,2013, 2014, 2015 ,2016, 2017,2018)) %>%
  count(MANDATE_START_YEAR, name = "frequency") %>%
    summarise(total_mandates=sum(frequency)) %>%
    arrange(desc(total_mandates))
View(most_mandates) 

mandato_p_ij_menos1<-mandato_p_ij[,-1]
View(mandato_p_ij_menos1) 
mandato_a_red_ij<-inner_join(mandato_a_red,mandato_p_ij_menos1, by=("PERSON_ID")) 
mandato_a_red_ij<-mandato_a_red_ij %>% distinct()
vis_miss(mandato_a_red_ij)

  multiple_mandates<-mandato_a_red_ij %>%
 select(PERSON_ID, MANDATE_ID, FIRSTNAME,LASTNAME,MANDATE_START_MONTH, MANDATE_START_YEAR,
        MANDATE_END_MONTH, MANDATE_END_YEAR) %>%
 group_by(PERSON_ID,MANDATE_ID,FIRSTNAME, LASTNAME) %>%
     filter(MANDATE_START_YEAR %in% c(1803,1805,1807,1808,1809,1811,1813,1814,1815,1816,1817,1818,1819,1820,1821,
1822,1823,1824,1825,1826,1827,182, 8,1829,1830,1831,1832,1833,1834,1835,1836,
1837,1838,1839,1840,1841,1842,1843,1844,1845,1846,1847,1848,1849,1850,1851,
1852,1853,1854,1855,1856,1857,1858,1859,1860,1861,1862,1863,1864,1865,1866,
1867,1868,18691870,1871,1872,1873,1874,1875,1876,1877,1878,1879,1880,1881,
1882,1883,1884,1885,1886,1887,1888,1889,1890,1891,1892,1893,1894,1895,1896,
1897,1898,1899,1900,1901,1902,1903,1904,1905,1906,1907,1908,1909,1928,1929,
1930,1931,1932,1933,1934,1935,1936,1937,1938,1939,1940,1941,1942,1943,1944,
1945,1946,1947,1948,1949,1950,1951,1952,1953,1954,1955,1956,1957,1958,1959,
1960,1961,1962,1963,1964,1965,1966,1967,1968,1969,1970,1971,1973,1974,1975,
1976,1977,1978,1979,1980,1981,1982,1983,1984,1985,1986,1987,1988,1989,1990,
1991,1992,1993,1994,1995,1996,1997,1998,1999,2000,2001,2002,2003,2004,2005,
2006,2007,2008,2009,2010,2011,2012,2013, 2014, 2015 ,2016, 2017,2018), 
MANDATE_END_YEAR %in% c(1803,1805,1807,1808,1809,1811,1813,1814,1815,1816,
1817,1818,1819,1820,1821,
1822,1823,1824,1825,1826,1827,182, 8,1829,1830,1831,1832,1833,1834,1835,1836,
1837,1838,1839,1840,1841,1842,1843,1844,1845,1846,1847,1848,1849,1850,1851,
1852,1853,1854,1855,1856,1857,1858,1859,1860,1861,1862,1863,1864,1865,1866,
1867,1868,18691870,1871,1872,1873,1874,1875,1876,1877,1878,1879,1880,1881,
1882,1883,1884,1885,1886,1887,1888,1889,1890,1891,1892,1893,1894,1895,1896,
1897,1898,1899,1900,1901,1902,1903,1904,1905,1906,1907,1908,1909,1928,1929,
1930,1931,1932,1933,1934,1935,1936,1937,1938,1939,1940,1941,1942,1943,1944,
1945,1946,1947,1948,1949,1950,1951,1952,1953,1954,1955,1956,1957,1958,1959,
1960,1961,1962,1963,1964,1965,1966,1967,1968,1969,1970,1971,1973,1974,1975,
1976,1977,1978,1979,1980,1981,1982,1983,1984,1985,1986,1987,1988,1989,1990,
1991,1992,1993,1994,1995,1996,1997,1998,1999,2000,2001,2002,2003,2004,2005,
2006,2007,2008,2009,2010,2011,2012,2013, 2014, 2015 ,2016, 2017,2018),
MANDATE_START_YEAR >= MANDATE_END_YEAR)%>%
  arrange(desc(MANDATE_START_YEAR))
  View(multiple_mandates)
  
  
  
  
  
mandato_p$PERSON_ID<-mandato_p$ID
View(mandato_p)
mandato_a_red_party<-mandato_a[,c(3:10)]
View(mandato_a_red_party)

mandato_ap_party<-full_join(mandato_a_red_party, mandato_p, by=("PERSON_ID"))
mandato_ap_party<- mandato_ap_party %>% distinct()

change_party<- mandato_ap_party %>%
select(PERSON_ID, FIRSTNAME, LASTNAME, PARTY, AFFILIATION_START_YEAR, AFFILIATION_END_YEAR) %>%   
group_by(PARTY,FIRSTNAME, LASTNAME) %>%
filter(AFFILIATION_START_YEAR %in% c(1803,1805,1807,1808,1809,1811,1813,1814,1815,1816,1817,1818,1819,1820,1821,
1822,1823,1824,1825,1826,1827,1828,1829,1830,1831,1832,1833,1834,1835,1836,
1837,1838,1839,1840,1841,1842,1843,1844,1845,1846,1847,1848,1849,1850,1851,
1852,1853,1854,1855,1856,1857,1858,1859,1860,1861,1862,1863,1864,1865,1866,
1867,1868,18691870,1871,1872,1873,1874,1875,1876,1877,1878,1879,1880,1881,
1882,1883,1884,1885,1886,1887,1888,1889,1890,1891,1892,1893,1894,1895,1896,
1897,1898,1899,1900,1901,1902,1903,1904,1905,1906,1907,1908,1909,1928,1929,
1930,1931,1932,1933,1934,1935,1936,1937,1938,1939,1940,1941,1942,1943,1944,
1945,1946,1947,1948,1949,1950,1951,1952,1953,1954,1955,1956,1957,1958,1959,
1960,1961,1962,1963,1964,1965,1966,1967,1968,1969,1970,1971,1973,1974,1975,
1976,1977,1978,1979,1980,1981,1982,1983,1984,1985,1986,1987,1988,1989,1990,
1991,1992,1993,1994,1995,1996,1997,1998,1999,2000,2001,2002,2003,2004,2005,
2006,2007,2008,2009,2010,2011,2012,2013, 2014, 2015 ,2016, 2017,2018)) %>%
count(AFFILIATION_START_YEAR, name="new_party") %>%
summarise(total_new_party=sum(new_party)) %>%
arrange(desc(total_new_party))
View(change_party)


`
```{r}

```

