---
title: "Rental Agency"
author: "Stefano Falconi"
date: "8/6/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
editor_options:
  chunk_output_type: console
---


The analysis of the data provided by the rental agency is explained in this 
report. Scrapping method was carried out with the use of R's "rvest"" 
package and selector gadget. Upon selection of the classes, the data was down-
loaded and filtered. Cleaning was done with the help of "gsub" function. 


Unfortunately, there was lots of missing data; in particular, variable "floor" 
accounted for approximately 36% of missing data. Out of 222 missing data for 
variable floor, approximately 16% belong to the postal codes from Genève and
they do not appear to follow any pattern. As it will be shown below, this 
variable does not seem to contribute much in the analysis. 

Visualization from both, "visdat" and "naniar" packages, proved to be handy in 
combination as far as missing data is concerned. Missing data for the dependent
variable “price” was relatively small, about 2.45%). One very important 
explanatory variable, "living-space", had also a relatively high proportion of
missing data (20.42%).

Postal code from the address is the only variable without missing data. 
Function "gsub" was straightforward and flexible enough for cleaning. 



```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(yaml)
library(rvest)
library(magrittr)
library(rebus)
library(stringr)
library(xml2)
library(photobiology)
library(formattable)
library(purrr)
library(knitr)
library(kableExtra)
library(data.table)
library(imputeTS)
library(visdat)
library(naniar)
library(readr)
library(stats)
library(DescTools)
library(sjmisc)
library(car)
library(e1071)
library(expss)

                                                                              
portal_address<-read_html('https://epfl-exts.github.io/rental-scrape/') %>%
  
html_nodes(".address") %>%
html_text()
portal_address<- as.character(gsub('\\s+',' ', portal_address))
View(portal_address)

portal_price<-read_html('https://epfl-exts.github.io/rental-scrape/') %>%
  
html_nodes(css= ".price")%>%
  html_text()
portal_price<- as.numeric(gsub('\\CHF',' ', portal_price))
View(portal_price)

portal_currency<-read_html('https://epfl-exts.github.io/rental-scrape/') %>%

html_nodes(".price")%>%
  html_text()
portal_currency<- as.character(gsub('[^CHF]','',portal_currency))
View(portal_currency)


portal_object_type<-read_html('https://epfl-exts.github.io/rental-scrape/') %>%

html_nodes(".object-type")%>%
  html_text()
portal_object_type<- as.character(gsub('\\s+',' ',portal_object_type))
View(portal_object_type)

portal_rooms<-read_html('https://epfl-exts.github.io/rental-scrape/') %>%

html_nodes(".rooms")%>%
  html_text()
portal_rooms<- as.numeric(gsub('\\Rooms',' ', portal_rooms))
portal_rooms<- round(portal_rooms, digits = 0)
View(portal_rooms)

portal_rooms_sinna<-na.omit(portal_rooms,na.action="omit",fill=NULL)
Mode(portal_rooms_sinna)

portal_living_space<-read_html('https://epfl-exts.github.io/rental-scrape/') %>%

html_nodes(".living-space")%>%
  html_text()
View(portal_living_space)

portal_living_space<- as.numeric(gsub('[\\Living space: m2]',' ',
portal_living_space))
View(portal_living_space)

portal_floor<-read_html('https://epfl-exts.github.io/rental-scrape/') %>%

html_nodes(".floor") %>%
  html_text()
portal_floor<- as.numeric(gsub('\\Floor:',' ',portal_floor))
View(portal_floor)

portal_floor_sinna<-na.omit(portal_floor,na.action="omit",fill=NULL)
Mode(portal_floor_sinna)
 

portal_availability<-read_html('https://epfl-exts.github.io/rental-scrape/') %>%

html_nodes(".availability")%>%
  html_text()
portal_availability<- as.character(gsub('\\s+',' ',portal_availability))
View(portal_availability)

portal_usable_surface<-read_html('https://epfl-exts.github.io/rental-scrape/')%>%

html_nodes(".usable-surface")%>%
  html_text()
portal_usable_surface<- as.character(gsub('\\Usable surface:',' ', 
portal_usable_surface))
View(portal_usable_surface)

rental<-data.frame(portal_address, portal_price, portal_currency, 
portal_object_type, portal_rooms, portal_living_space, portal_floor,
portal_availability, portal_usable_surface)
View(rental)


col.from<-c("portal_address", "portal_price", "portal_currency",
"portal_object_type", "portal_rooms", "portal_living_space",
"portal_floor", "portal_availability", "portal_usable_surface")
col.to<-c("address","price","currency", "object_type", "rooms",
"living_space_m2", "floor", "availability", "usable_surface")

names(rental)[match(col.from, names(rental))]<- col.to 
View(rental) 
vis_dat(rental)
vis_miss(rental)
table(is.na(rental$price))
table(is.na(rental$living_space_m2))
table(is.na(rental$floor))




```

The imputation package "imputeTS" and its "frequency" algorithm provided the 
missing numbers for “price” and “living-space-m2 (there was the option in the 
use of another algorithm, from the "mice" package but this method generated 
more zero values than the imputeTS's package. As will be seen shortly, zero 
values generate indeterminate values when used as an argument for the 
logarithmic function).

For variables "floor" and “room”, the mode of "1" and “4”, respectively, 
were the reference for imputation.  Function "replace.na" provided with 
missing values for the latter.  

Before graphing the scatter plot of "price-living_space", it is essential 
to mention how the variables behave individually. The idea is betteer 
illustrated with histogram plots.

If the histograms for prices and living-space_m2 are plotted, data will be 
positive skewed. The interpretation for this is that there are a high number 
of houses and appartments similar in prices and living areas but only few 
places are in the other extreme of surface areas and price range. The plot
will clarify this comment and reinforce the concept just mentioned.

Take notice the lower left part of the plot. Most datapoints are clustered 
between 1 and 190 m² and 1 and 10000 CHF. As for any trend, by adding a
smoothed line to the plot, it it much to see it.

As for the number of rooms, most houses and apartments have between 1-4 rooms 
with a higher number of places with 1 to 2 rooms. Unlike the living-space 
data, no such extremes are observed in the rooms variable. It is for this 
reason that rooms' data has a relatively normal distribution shape. This can
be observed in the histogram  plots, completely different from price, space 
and number of floors.







```{r echo =FALSE, message=FALSE, warning=FALSE}

rental_tb<-as_tibble(rental) 
  price_imputed<-na_seadec(rental_tb$price, algorithm = "interpolation", 
find_frequency = TRUE, maxgap = Inf)
price_imputed<-round(price_imputed, digits = 2)
space_imputed<-na_seadec(rental_tb$living_space_m2, algorithm =
"interpolation", find_frequency = TRUE, maxgap = Inf)
space_imputed<-round(space_imputed, digits = 2)


floor_imputed<-replace_na(rental_tb$floor, value= 1)
floor_imputed

rental_tb$floor_imputed<-round(floor_imputed, digits = 0)
rental_tb$floor_imputed

rooms_imputed<-replace_na(rental_tb$rooms,value = 4)

table(is.na(price_imputed))
table(is.na(space_imputed))
table(is.na(floor_imputed))



listado<-rental_tb$address %>% str_match_all("[0-9]+") %>% unlist %>% as.numeric
listado_df<-data.frame(listado)
listado_postal<-listado_df %>% filter(listado > 1000)
listado_v<-as_vector(listado_postal)
rental_tb$postalcod<-listado_v
View(rental_tb)

rental_tbl<- rental_tb %>%
mutate(price_imputed, rooms_imputed, space_imputed, floor_imputed, postalcod)
View(rental_tbl)

write_csv(rental_tbl,  "rental_tbl.csv",
quote_escape = "double")


rental_tbl %>% ggplot(aes(x = space_imputed, y = price_imputed)) +
     geom_point(colour = "purple",
                size = 4,
                alpha = 0.5) +
     labs(title = "Price vs. Living space",
          caption = "Living space as a function of surface area ",
          x = "Space (m2)",
          y = "Value amount (CHF)") +
     theme_minimal()


qplot(carat, price, data = dsmall, geom = c("smooth", "point"))




```
The scatter plot depicts some sort of a positive relationship. In order to 
describe such association, two linear regressions were run. One included the 
price_imputed and living_space_m2 variables, the other model was a double-log 
function. The rationale for chosing this functional form is the skewness equals 
2 for both variables. 



```{r echo =FALSE}


skewness(rental_tbl$price_imputed, na.rm= FALSE, type= 3)

rental_tbl %>% ggplot(aes(x=price_imputed)) +
  geom_histogram(aes(y = ..density..),
                 bins = 20,
                color= "black",
                 fill = "blue",
                 alpha= 0.3) +
   geom_density() +
  labs(title = "Skewness of Variable Price of Rent",
                caption = "Rental prices in local market",
                x= "CHF ($)",
                y = "Frequency") +
    theme_minimal()            


skewness(rental_tbl$space_imputed, na.rm= FALSE, type= 3)

rental_tbl %>% ggplot(aes(x=space_imputed)) +
  geom_histogram(aes(y = ..density..),
                 bins = 20,
                color= "black",
                 fill = "green",
                 alpha= 0.3) +
   geom_density() +
  labs(title = "Skewness of Variable Living Space in m2",
                caption = "Rental prices in local market",
                x= "CHF ($)",
                y = "Frequency") +
    theme_minimal()            




skewness(rental_tbl$rooms_imputed, na.rm= FALSE, type= 3)

rental_tbl %>% ggplot(aes(x=rooms_imputed)) +
  geom_histogram(aes(y = ..density..),
                 bins = 20,
                color= "black",
                 fill = "yellow",
                 alpha= 0.3) +
   geom_density() +
  labs(title = "Skewness of Variable Rooms",
                caption = "Rental prices in local market",
                x= "CHF ($)",
                y = "Frequency") +
    theme_minimal()            


skewness(rental_tbl$floor_imputed, na.rm = FALSE, type=3)


rental_tbl %>% ggplot(aes(x=floor_imputed)) +
  geom_histogram(aes(y = ..density..),
                 bins = 20,
                color= "black",
                 fill = "brown",
                 alpha= 0.3) +
   geom_density() +
  labs(title = "Skewness of Variable Floor",
                caption = "Rental prices in local market",
                x= "CHF ($)",
                y = "Frequency") +
    theme_minimal()            


```


A double log model indicates the percentage change of the dependant variable for 
every percentage unit of change of the explanatory variable. The 0.2321 coefficient 
of living-space_m2 is interpreted in the following fashion: For every 1% change in 
squared maters for the living-space, the rental price changes by about 23.21%. 
Specifically, for every 23.21% increment in squared meters of space, the rental 
price's increment is approximately 5%. It is calculated as it follows: 
((1.2321^0.2321)- 1)*100. 




```{r echo =FALSE}

 rental_tbl_no0<-subset(rental_tbl, space_imputed!=0)
 rental_tbl_no0$priceln<-log(rental_tbl_no0$price_imputed)
 
rental_tbl_no0$spaceln<-log(rental_tbl_no0$space_imputed)
View(rental_tbl_no0)
model_priceln_spaceln<-lm(priceln ~ spaceln, data =rental_tbl_no0) 
summary(model_priceln_spaceln)
Coefint_priceln_spaceln<-confint(model_priceln_spaceln, level=0.95)
Coefint_priceln_spaceln


model_price_space<-lm(price_imputed ~ space_imputed, data=rental_tbl)
summary(model_price_space)
Coefint_price_space<-confint(model_price_space, level=0.95)
Coefint_price_space



```

For the second model, for every increase of 1 m² in living space, rental 
price incremented accordingly to 14 CHF.

For both models the coefficients have the correct positive signs and they have 
statistical significance at 0.1%, 0.01%, and 0.05% levels. Take notice both 
confidence intervals do not include the zero value, supporting the p-value.


The table below shows the coefficients, the R² adjusted-value,  the p-value and 
the confidence intervals (CI). Both models have relatively low R2 adjusted-value. 
In addition for indicating how well the data points fit well the curve, the 
R2 adjusted value would increase when proper variables are included; otherwise
would decrease when variables are useless.

```{r echo =FALSE} 
 Table1<-data.frame("Models" = c("model_price_ln_space_ln","model_price_space"), "intercept"=c(7.1042, 2712.907), "coefficient" = c(0.2321,14.255), "R2_adj" = c(0.1239,0.1735), "CI_inf"=c(0.1825067, 11.79426), "CI_sup"=c(0.2817, 16.715), stringsAsFactors = FALSE)

View(Table1)
```

The following table shows the distribution of properties according to postal
code
```{r echo =FALSE}
postal_codes <- rental_tbl %>%
     count(postalcod, name = "properties")
View(postal_codes)
 
 postal_codes %>% ggplot(aes(x = postalcod, y = properties , fill = postalcod)) +
    geom_col(alpha = 0.7, col="orange") +
    labs(title = "Number of Properties by Postal Codes",
         caption = "Most activity of agency seems to be at Genève",
         x = "Location",
         y = "Frequency") +
    theme_minimal() +
    theme(legend.position = "none")
 
 
 geneve<- postal_codes %>%
 filter(postalcod %in% c(seq(1200,1209,1)))%>%
 summarize(sum(properties))
 geneve
 


na_geneve<-  rental_tbl %>%
select(floor, postalcod) %>%
filter(postalcod %in% c(seq(1200,1209,1)))
View(na_geneve)
table(na_geneve$floor=="NA")
 

```

It can be seen in the last plot that most of the activity of the agency takes
place at Genève. The table above exhibits the distribution of properties for 
the 56 postal codes of which 300 properties were rented in that city. There 
are also included two llustrative plots showing with the  geom_miss_point" 
function the activity for the 56 postal codes, for both cases, with missing 
data and non-missing data. These plots show an upward-sloped movement in the
dots from the small plots. A different pattern is observed in  the remaining
46 plots (different cities).

The last plot shows price, space, number of floors, and location of property.

It would be interesting to analize further variables that could possibly exert
some influence in the rental price such as: distance to shopping centers or 
downtown, age of apartment, noise, pollution, etc.


```{r echo =FALSE}

rental_tbl %>% ggplot(aes(x=living_space_m2, y=price))+
  geom_miss_point()+
  facet_wrap(~postalcod)

rental_tbl %>% ggplot(aes(x=space_imputed, y=price_imputed))+
  geom_miss_point()+
  facet_wrap(~postalcod)




 rental_tbl_all<-rental_tbl %>%
 pivot_longer(
   cols = c(postalcod, floor_imputed),
   names_to = "profile",
   values_to = "info")
 View(rental_tbl_all)
 
 
 
 ggplot(rental_tbl_all, aes(x=space_imputed, y=price_imputed, fill=profile)) +
   geom_bar(position = "stack", stat = "identity") + geom_point(colour = "purple",
                size = 0.75,
                alpha = 0.5) +
    facet_wrap(~ profile+info) +
     labs(title = "Price vs. Living space, postal code and number of floors",
          caption = "Rental prices (place, space, and number of floors)",
          x = "Area (m²)",
          y = "Value (CHF)") +
     theme(text=element_text(size=8), axis.text.x=element_text(angle=45, hjust=1))

```

